### 2012-11-15 ASA2013/asa2013.tex
la2pdf commit - 2012:11:15	13:27:01	(Thu15.Nov)

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but relies on the estimation and inversion of a spatial covariance for each image pixel. This translates to a computational complexity that is cubic with number of channels.

For systems with less than 32 channels, we suggest arithmetic optimizations for the estimation step, and explain how the MVDR can be mapped to a high-end GPU to yield processing rates of more than 1\,Mpx/s. When $M$ exceeds 32, we show that frequency domain processing can be employed instead, which allows a comparable performance to be maintained, at a neglible reduction in image quality. Compared to our reference C and Matlab implementation, the GPU implementation offered a speedup of 2-3 orders of magnitude, but at the expense of a non-trivial design.

A very good alternative to the MVDR is the Low Complexity Adaptive beamformer (LCA). It does not compute a weightset, but merely computes the beamformer output for each of a each predefined set of weights, and selects the one that best fulfills the MVDR criteria. The images it produces are comparable to the MVDR, without the development cost or complexity of the MVDR, and it is perfectly suited for a GPU.

\ \\
Total: 239 words (200 max)

\ \\
Noen tanker jeg har selv nå:
\begin{itemize}
\item Dette blir mye beamforming, beamforming, beamforming. Mulig jeg må riste av meg ``JOE formen'' og fokusere litt mer på implementasjonsaspektet.
\item Det er mye ord, og litt muntlig. Det går seg til så snart jeg har bestemt meg for innhold.
\item Det mangler noe om bruksområder.
\item Må passe på å ikke selge LCA så bra at MVDR ser helt håpløs ut(?)
\item 200 ord er ingenting. :)
\end{itemize}

>>>>

\begin{abstract}
The MVDR adaptive beamformer has lately been shown to improve image quality in active sonar systems, but at a major computational expense. This is because the estimation and inversion of a spatial covariance matrix is required for each image pixel. We target this problem by altering and mapping the MVDR algorithm GPU, and suggest three different solutions depending on the system size.

For systems with less than 32 channels, we suggest arithmetic optimizations for the estimation step, and show how a careful mapping to a high-end GPU to yield processing rates of more than 1\,Mpx/s. When the system exceeds this size, we show that frequency domain processing can be employed instead, which allows a comparable performance to be maintained, at a neglible reduction in image quality. These GPU implementations consistently reduced the runtime by 2-3 orders of magnitude compared to our reference C and Matlab implementations.

Should this this still be insufficient, we suggest having a look that the LCA beamformer. It does not compute a weightset, but merely computes the beamformer output for each of a each predefined set of weights, and selects the one that best fulfills the MVDR criteria. The images it produces are comparable to the MVDR, without the development cost or complexity of the MVDR, and it is perfectly suited for a GPU.

\ \\
Total: 215 words (200 max)

\ \\
Noen tanker jeg har selv nå:
\begin{itemize}
\item Det mangler noe om bruksområder.
\item Må passe på å ikke selge LCA så bra at MVDR ser helt håpløs ut(?)
\item 200 ord er ingenting. :)
\end{itemize}
